Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-29 paper/AlignedIsotropicGW.tex
As submitted to DCC.
Back to red "checkme" numbers now that DCC submission has been generated.

\newcommand{\checkme}[1]{\textcolor{red}{#1}}

@@

The distributions in Eq.\ \eqref{eq:magnitude-dists} are not meant to
represent any particular physical model, but rather to capture our
uncertainty about the spin magnitude distribution, discussed in detail
in Section \ref{sec:discussion}; neither observations nor population
synthesis codes can at this point authoritatively suggest {\it any}
particular spin distribution.  Our models, however, allow us to see
how sensitive the $\chieff$ distribution is to spin alignment given
uncertainties about the spin magnitudes.

>>>>

\newcommand{\checkme}[1]{\textcolor{red}{#1}}
%\newcommand{\checkme}[1]{ #1 }

@@

The distributions in Eq.\ \eqref{eq:magnitude-dists} are not meant to
represent any particular physical model, but rather to capture our
uncertainty about the spin magnitude distribution, discussed in detail
in Section \ref{sec:discussion}; neither observations nor population
synthesis codes can at this point authoritatively suggest {\it any}
particular spin distribution \citep{2015PhR...548....1M}.  Our models,
however, allow us to see how sensitive the $\chieff$ distribution is
to spin alignment given uncertainties about the spin magnitudes.
